Estimating migration rates for iteroparous species using kinship pairs found between populations

### 2022-01-11 latex/ms.tex
modify novelty, #14

>>>>

We presented mainly three novel points in this paper. First, we formulated probabilities of kinship pairs randomly chosen between two populations ($\pi_{\rm HS,bet}$ and $\pi_{\rm PO,bet}$), which provide estimators of the migration number or rate. While similar derivations are found in the context of a mark-recapture method (REF), these are limited to the situation such that sampling can be non-invasive and adult individuals are sampled. Our proposed method can avoid these limitations, where such advantages are generally characterized in CKMR method. Second, we revealed that the probabilities of kinship pairs are approximately independent of reproductive potential and thus information about it is not needed for the estimation, if migration event and the potential are independent. This is a useful property of the estimators because heterogeneity of reproductive potential within/between populations are generally observed in iteroprous species. Third, we demonstrate applicability that the estimation can be obtained only from the genetic data, and there are numerous advantages in using the proposed estimator instead of separately estimating $\pi_{\rm HS,bet}$ (and/or $\pi_{\rm PO,bet}$) (via genetic method) and $N_1$ (and/or $N_2$) (via nongenetical method).
